---
title: "Cross Validation"
output: github_document
---

```{r setup}
library(tidyverse)
library(modelr)
library(mgcv)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = 0.6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Simulated dataset
```{r}
nonlin_df = 
  tibble(
    id = 1:100,
    x = runif(100, 0, 1),
    y = 1 - 10 * (x - .3) ^ 2 + rnorm(100, 0, .3)
  )
```

Look at the data 

```{r}
nonlin_df %>% 
  ggplot(aes(x = x, y = y)) +
  geom_point()
```


## Cross- validation by hand 

Generate a training dataset and a testing dataset 

```{r}
train_df = sample_n(nonlin_df, size = 80)
test_df = anti_join(nonlin_df, train_df, by = "id")
```

Fit three models.

```{r}
linear_model = lm(y ~x, data = train_df)
smooth_mod = gam(y ~ s(x), data = train_df)
wiggly_mod = gam(y ~ s(x, k = 30), sp = 10e-6, data = train_df)
```

Can I see what I just did ?

```{r}
train_df %>%
  gather_predictions(linear_model, smooth_mod, wiggly_mod) %>% 
  ggplot(aes(x = x, y = y)) +
  geom_point() +
  geom_line(aes(y = pred), color = "red") + 
  facet_grid(. ~ model)
```

The smooth model does best for prediction accuracy ! 

Look at prediction accuracy - (computing the root mean sq for these model)
- use the testing dataset 

```{r}
rmse(linear_model, data = test_df)
rmse(smooth_mod, data = test_df)
rmse(wiggly_mod, data = test_df)
```

This is what cross validation does - picks the smooth model to pick the best model to make a prediction. 

used when we are looking at unnested datasets.

## Cross validation using `modelr`

```{r}
cv_df = 
  crossv_mc(nonlin_df, 100)
```

what is happening here ?

```{r}
cv_df %>%  pull(train) %>% .[[1]] %>% as_tibble()
cv_df %>%  pull(test) %>% .[[1]] %>% as_tibble()
```

```{r}
cv_df = 
  cv_df %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble)
  )
```

Let's try to fit models and get RSME for them 

```{r}
cv_df = 
cv_df %>% 
  mutate(
    linear_model =  map(.x = train, ~lm(y ~ x, data = .x)),
    smooth_mod = map(.x = train, ~ gam(y ~ s(x), data = .x)),
    wiggly_mod = map(.x = train, ~gam(y ~ s(x, k = 30), sp = 10e-6, data = .x))
  ) %>% 
  mutate(
    rmse_linear = map2_dbl(.x  = linear_model, .y = test, ~rmse(model = .x, data = .y)),
    rmse_smooth = map2_dbl(.x  = smooth_mod, .y = test, ~rmse(model = .x, data = .y)),
    rmse_wiggly = map2_dbl(.x  = wiggly_mod, .y = test, ~rmse(model = .x, data = .y))
  )
```

Produce the RMSE that corresponds to each of these. 

What do these results say about model choice

```{r}
cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model",
    values_to = "rmse",
    names_prefix = "rmse_"
  ) %>% 
  ggplot(aes(x = model, y = rmse)) +
  geom_violin()
```

Based on the distribution of the rmse and the plots - we can say that the smooth model is doing the best. 

compute averages... 

```{r}
cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model",
    values_to = "rmse",
    names_prefix = "rmse_"
  ) %>% 
  group_by(model) %>% 
  summarize(avg_rmse = mean(rmse))
```

smooth is the lowest, hence does better than the other two !

